Everything I know about Subset Sum Reconfiguration

### 2013-07-18 notes/ssr.tex
Add a little more explanation

\noindent In some cases we can iterate Lemma~\ref{lemma:reduction} to reduce the instance to the trivial one-element case.
\begin{prop}\label{prop:iterated-reduction}
    Suppose we have an SSR instance with element set $E$, threshold $k$ and capacity $c$. Suppose further that no element weighs more than $c-k$. Let $E = {e_0, \dots, e_n}$ in nondecreasing order by weight. If
    \[
        w(e_i) < c - k + \sum_{j<i}w(e_j) - w(e_n) + 2
    \]
    for all $i$ then the instance is solvable. Note that this condition does not mention the start or target packings, so in fact such instances have the property that any valid packing is reachable from any other.
\end{prop}
\begin{rem}
    Let us say that an instance satisfying the property of Proposition~\ref{prop:iterated-reduction} is \textit{completely reducible}. The instances exhibited in Proposition~\ref{prop:element-moves-a-lot} are completely reducible. The instances exhibited in Proposition~\ref{prop:quadratic-bound} are not completely reducible, but can be reduced to a form that has a linear bound on the length of the solution sequence.
\end{rem}
\end{document}

>>>>

\noindent In some cases we can iterate Lemma~\ref{lemma:reduction} to reduce the instance to the trivial one-element case.
\begin{prop}\label{prop:iterated-reduction}
    Suppose we have an SSR instance with element set $E$, threshold $k$ and capacity $c$. Suppose further that no element weighs more than $c-k$. Let $E = {e_0, \dots, e_n}$ in nondecreasing order by weight. If
    \[
        w(e_i) < c - k + \sum_{j<i}w(e_j) - w(e_n) + 2
    \]
    for all $i$ then the instance is solvable. Note that this condition does not mention the start or target packings, so in fact such instances have the property that any valid packing is reachable from any other.
\end{prop}
\begin{rem}
    Let us say that an instance satisfying the property of Proposition~\ref{prop:iterated-reduction} is \textit{completely reducible}. The instances exhibited in Proposition~\ref{prop:element-moves-a-lot} are completely reducible. The instances exhibited in Proposition~\ref{prop:quadratic-bound} are not completely reducible, but can be reduced to a form that has a linear bound on the length of the solution sequence by eliminating the elements that have weight $1$.
\end{rem}
\end{document}
